A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-14 article/02_Materials_and_Methods.Rmd
added reference to my master thesis

The analysis code of this paper is written in the statistics programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible: **doi**. A more in-depth description and discussion of the data preparation can be found in the master thesis this article is based on **TODO**.

>>>>

The analysis code of this paper is written in the statistics programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible: **doi**. A more in-depth description and discussion of the data preparation can be found in the master thesis this article is based on [@schmidComputerbasiertesCulturalEvolution2018].
